Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
More explanations

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism or target architecture might place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers have their values maintained by whichever compiler
generated their code. Our properties explicitly state this as a requirement,
which could be enforced by a micro-policy, a well-behaved compiler, or other enforcement technique.

@@

To characterize confidentiality\apt{and sometimes integrity}, we borrow the idea of \emph{variant} states
from the theory of non-interference. Non-interference is a way of expressing
the flow of information through the system. If we begin with a state \(\mach\)
and modify it to \(\nach = \mach[\component \mapsto v]\) for arbitrary \(v\),
then execute both \(\mach\) and \(\nach\), any differences in the outputs they
produce must be the result of accessing \(\component\).

@@

\apt{needs small transition}

@@

The system we model in \cref{sec:example,sec:formal} is very simple, but our properties
support an important dimension of generality: adding features.\apt{Just what needs to be changed
to add these features?}
We now briefly introduce the features of our primary testing machine.\apt{Make sure
testing has been introduced properly before now. And why ``primary''?}

The full machine defines additional operations, and extends some of the old ones.
We add a field \(\overline{sa}\) to the \(\mathbf{call}\) operation: a set of
triples of a register \(\reg\), a base offset \(\mathit{off}\), and a size \(sz\), denoting
that the value at the offset \(\mathit{off}\) from \(\reg\) is to be passed as an argument.
The new \(\mathbf{tailcall}\) operation has the same fields, but deals with tail-call
optimizations in which the callee will reuse the caller's stack. The \(\mathbf{alloc}\) operation
gains a boolen flag indicating whether the allocation is to be public, accessible to
all functions until deallocated. The rules are given in \cref{fig:advops}; the
rules in \cref{fig:basicops} can be recaptured by instantiating
\(\mathbf{call}\) with \(\overline{sa}\) as the empty set, and \(\mathbf{alloc}\)
with flag \(\mathbf{f}\).

@@

Using this mechanism, an call-by-value argument passed on the stack at an \(\SP\)-relative offset
is specified by the triple \((\SP, \mathit{off}, \mathit{sz})\).
In this case, only the immediate callee gains access to the argument location.
A C++-style call-by-reference argument where the reference is passed in \(\reg\)
is instead specified by \((\reg, 0, \mathit{sz})\), which allows
the reference to be passed further down the stack.
\apt{What if the reference is itself passed on the stack?}
%In this second case, the reference can be passed further down the stack, but otherwise
%only the immediate callee gains access. APT:

@@

Since the caller will not be returned to, it does not need integrity, but
it should still enjoy confidentiality. We set its frame to \(\unsealed\) rather
than \(\sealed\) to express this.

\apt{good place to detail the needed changes in interpretation of \cref{tab:props}.}

@@

Roessler and DeHon do not protect registers, but we consider registers to be
an extension of the stack. In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.
\apt{Presumably R\&dH don't care about registers because they already have
  the compiler in the TCB.  We should note (perhaps earlier than here!) that
  we have a stronger attacker model since we don't require the callee code
  to come from a trusted  compiler.}

>>>>

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism or target architecture might place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers have their values maintained by whichever compiler
generated their code. Our properties explicitly state this as a requirement,
which could be enforced by a micro-policy, a well-behaved compiler, or other enforcement technique.
Roessler and DeHon have the compiler in their trusted computing base, so our properties
are stronger than necessary to characterize their micro-policies.

@@

To characterize situations in which values should be kept secret or prevented
from influencing future execution, we borrow the idea of \emph{variant} states
from the theory of non-interference. Non-interference is a way of expressing
the flow of information through the system. If we begin with a state \(\mach\)
and modify it to \(\nach = \mach[\component \mapsto v]\) for arbitrary \(v\),
then execute both \(\mach\) and \(\nach\), any differences in the outputs they
produce leaks information about \(\component\).

@@

When comparing the behavior of variant states, we need a notion of how their
differences have influenced them.

@@

The system we model in \cref{sec:example,sec:formal} is very simple, but our properties
are designed to make it easy to add features. To support argument passing on the stack,
we just new parameters to the existing security-relevant operations, and refine how they
update the security context. The remainder of the properties do not change at all.
To add tail-calls, we add and define a new operation, and since it is a kind of call,
we add it to the definition of call targets again.
The rules for the expanded machine are given in \cref{fig:advops}; the
rules in \cref{fig:basicops} can be recaptured by instantiating
\(\mathbf{call}\) with \(\overline{sa}\) as the empty set, and \(\mathbf{alloc}\)
with flag \(\mathbf{f}\).

@@

Using this mechanism, an call-by-value argument passed on the stack at an \(\SP\)-relative offset
is specified by the triple \((\SP, \mathit{off}, \mathit{sz})\).
In this case, only the immediate callee gains access to the argument location.
A C++-style call-by-reference argument where the reference is passed in \(\reg\)
is instead specified by \((\reg, 0, \mathit{sz})\), which allows
the reference to be passed further down the stack.
\apt{What if the reference is itself passed on the stack?}
\sna{Ugh. We could make \(\reg\) an arbitrary element, but that seems like it's getting
  dangerously close to indirection.}

@@

Since the caller will not be returned to, it does not need integrity, but
it should still enjoy confidentiality. We set its frame to \(\unsealed\) rather
than \(\sealed\) to express this. In terms of \cref{tab:props}, we replace
``call'' with ``call or tailcall'' in \(\clrc\), \(\clec\), and \(\clei\).

@@

Roessler and DeHon do not protect registers, since the compiler is in the
trusted computing base, but we support threat models that do not.
In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.
